Supplementary tables and figures for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-17 src/docs_paper/tables-figures.Rmd
Add model direct benefits plot #128
Tables and figures in appendices A and B now have appropriate "A." or "B." prefixes to distinguish from those in the main text #128

>>>>

<!-- So that the tables and figures in this appendix are prefixed by "B." -->
\setcounter{table}{0}  
\renewcommand{\thetable}{B.\arabic{table}} 
\setcounter{figure}{0} 
\renewcommand{\thefigure}{B.\arabic{figure}}

# Additional figures

<!-- Might find a home for these. -->

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group. Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district level heterogeneity, as well as imputing any districts with missing data.}
\label{fig:model-direct-benefits}
\end{figure}
